---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sequenceR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/sequenceR)](https://CRAN.R-project.org/package=sequenceR)
[![R-CMD-check](https://github.com/JamiePlace/sequenceR/workflows/R-CMD-check/badge.svg)](https://github.com/JamiePlace/sequenceR/actions)
<!-- badges: end -->

The goal of sequenceR is to identify sequences of 1's in a vector of 1's and 0's. The problem stems from needing to find such sequences efficiently in a simulation environment. 

seqeunceR utilises the efficient convolution processes from the [torch](https://torch.mlverse.org/packages/) package 

## Installation

You can install the released version of sequenceR from [github](https://github.com/JamiePlace/sequenceR) with:

``` r
devtools::install_github("JamiePlace/sequenceR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sequenceR)

sequence_data <- c(0,0,0,1,1,1,0,1,0,1,0,1,1,1)

window <- 3

find_sequences(sequence_data, window = window)
```

The output is a vector with length equal to that of the given vector with 1's in the location where a sequence matching the requirements begins
